Efficiently stable presentations from error-correcting codes

### 2023-11-02 efficient_stability.tex
Updates from Overleaf

We make an observation that connects the study of testable codes to questions of stability in group theory and motivates our work. Let $\code=\ker h$ be a linear code as above, and suppose for simplicity that $\F=\F_2$ is the binary field. Consider the finitely presented group 
\begin{align}
 G(h) \,=\, \langle S:R\rangle \,=\, \big\langle &x_1,\ldots,x_n \,:\quad  x_j^2=e\quad \forall 1\leq j\leq n\;,\notag\\
& \quad \prod_{1\leq j \leq n} x_j^{h_{ij}} = e\;,\quad [x_{j_1},x_{j_2}]^{h_{ij_1} h_{ij_2}}=e\quad \forall 1\leq i\leq m\,\forall 1\leq j_1,j_2\leq n\,\big\rangle\;.\label{eq:gh-intro}
\end{align}
Here a commutation relation between two generators  $[x_{j_1},x_{j_2}]=e$ is imposed only when needed for the relations $\prod_{1\leq j \leq n} x_j^{h_{ij}} = e$ to make sense, i.e.\ two generators are required to commute only if they both take part in the same equation, which is the case if and only if $h_{ij_1}h_{ij_2}=1$ for some $i$. \tnote{added:}While one could add all pairwise commutation relations, forcing $G(h)$ to be abelian --- and indeed we will do this in some cases later --- we choose the specific presentation~\eqref{eq:gh-intro} for consistency with the literature on non-local games, and particularly so-called \emph{linear constraint system games}, which we review in more detail below.

>>>>

We make an observation that connects the study of testable codes to questions of stability in group theory and motivates our work. Let $\code=\ker h$ be a linear code as above, and suppose for simplicity that $\F=\F_2$ is the binary field. Consider the finitely presented group 
\begin{align}
 G(h) \,=\, \langle S:R\rangle \,=\, \big\langle &x_1,\ldots,x_n \,:\quad  x_j^2=e\quad \forall 1\leq j\leq n\;,\notag\\
& \quad \prod_{1\leq j \leq n} x_j^{h_{ij}} = e\;,\quad [x_{j_1},x_{j_2}]^{h_{ij_1} h_{ij_2}}=e\quad \forall 1\leq i\leq m\,\forall 1\leq j_1,j_2\leq n\,\big\rangle\;.\label{eq:gh-intro}
\end{align}
Here a commutation relation between two generators  $[x_{j_1},x_{j_2}]=e$ is imposed only when needed for the relations $\prod_{1\leq j \leq n} x_j^{h_{ij}} = e$ to make sense, i.e.\ two generators are required to commute only if they both take part in the same equation, which is the case if and only if $h_{ij_1}h_{ij_2}=1$ for some $i$. While one could add all pairwise commutation relations, forcing $G(h)$ to be abelian --- and indeed we will do this in some cases later --- we choose the specific presentation~\eqref{eq:gh-intro} for consistency with the literature on non-local games, and particularly so-called \emph{linear constraint system games}, which we review in more detail below.
